The Functional Therapeutic Chemical Classification System

### 2013-08-19 document.tex
caption figure 1
Signed-off-by: loopasam <samuel.croset@gmail.com>

\begin{figure*}[!tpb]%figure1
\centerline{\includegraphics{fig1.png}}
\caption{Summary of the methodology used to construct the resource. The FTC categories are first created (A) from the existing GO terms
describing molecular functions and biological processes. Then, each category has an equivalent definition assign to it (B).
The content of various databases in incorporated (C) and linked using the FTC specific properties. Finally a reasoner runs over the knowledge
base and assigns drugs to MoA categories based on whether or not a definition can be satisfied.}\label{fig:01}
\end{figure*}

>>>>

\begin{figure*}[!tpb]%figure1
\centerline{\includegraphics{fig1.png}}
\caption{Summary of the methodology used to construct the resource. (A) The FTC categories are first created from the existing GO terms
describing molecular functions and biological processes. (B) Then, each category has an equivalent definition assign to it.
(C) The content of various databases in incorporated and linked using the FTC specific properties. (D) Finally a reasoner runs over the knowledge
base and assigns drugs to MoA categories based on whether or not a definition can be satisfied.}\label{fig:01}
\end{figure*}
